Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-31 paper-arxiv-v1/sec-conclusions.tex
Added v2 of paper in repo

In this work we have presented a feasibility study for
 the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the LHC.
%
Our strategy is based on the combination of traditional
cut-based analysis with state-of-the-art multivariate techniques.
%
We take into account 
all relevant backgrounds, in particular
the irreducible $4b$
and the reducible 
$2b2j$ and $4j$ QCD multijets.
%
We have illustrated how the $2b2j$ component leads to
a contribution comparable to that of the $4b$ process,
due to a combination of  parton shower effects, $b$-quark 
pair radiation, and selection requirements.
%
We have also demonstrated the robustness of our analysis strategy
under the addition of significant PU.

Combining the contributions from the resolved,
intermediate and boosted categories, we find that, for
$\mathcal{L}=3$ ab$^{-1}$, the
signal significance for
the production of Higgs pairs can be as large as $S/\sqrt{B}\simeq 7$.
%
This indicates that, already from the $b\bar{b}b\bar{b}$
final state alone,
it should be possible to claim discovery of Higgs pair production at
the HL-LHC.
%
Our study also suggests possible avenues that the LHC experiments
could explore to further improve this signal significance.
%
One handle would be to reduce the contribution from light and charm
jet mis-identification, ensuring that the irreducible $4b$ background 
 dominates over the $2b2j$ component.
%
Another possibility would be to improve the mass resolution of the Higgs
reconstruction
in high-PU environments, and, more in general,
to optimize the PU subtraction
strategy in order
to reduce the impact of PU in the modelling
of kinematical variables and the associated
degradation in the MVA discrimination.
%
Such experimental improvements might
even make possible
an observation of Higgs pair production at the
end of Run II with
$\mathcal{L}=300$ fb$^{-1}$.

Another challenging aspect of the measurement of Higgs pairs
in the $b\bar{b}b\bar{b}$ final state is achieving an efficient
triggering strategy.
%
In order to reduce the rate from background QCD processes sufficiently, while
being able
to access the relevant $p_T$ regimes, (multi-)jet triggers
using $b$-quark tagging information online for one or more jets are
likely to be
necessary.
%
The additional rejection provided by these triggers could
enable events to be selected efficiently, with four
jets down to $p_T=45$ GeV in the resolved category,
and boosted Higgs decays in large-$R$ jets down to jet transverse momenta of
$p_T=200$ GeV.

One important implication of this work is that it should
be possible to significantly
improve  the accuracy on the extraction of
the Higgs trilinear coupling $\lambda$ from
a measurement of the
$\sigma\lp hh\to b\bar{b}b\bar{b}\rp$ cross-section, as compared
to existing estimates.
%
A determination of $\lambda$ in our approach is however
rather
non-trivial, involving
 not only regenerating signal samples
 for a wide range of values of  $\lambda$, but also
 repeating the analysis
optimisation, including the MVA training, for each
of these values.
%
This study is left to a future
publication, where we will also
compare with the corresponding  precision 
that has been reported from other final states such as
 $b\bar{b}\gamma\gamma$
and $b\bar{b}\tau\tau$.
%
It will also be  interesting to perform
this exercise for a 100 TeV hadron collider~\cite{Barr:2014sga,
  Azatov:2015oxa,Papaefstathiou:2015iba,
  Arkani-Hamed:2015vfh}.
%
While at 100 TeV the
signal yields would be increased, also the (gluon-driven) QCD
multijet background would grow strongly.
%
Revisiting
the present analysis, including the MVA optimization,
at 100 TeV would also allow
to assess the accuracy of an extraction of the trilinear
coupling $\lambda$ from the $b\bar{b}b\bar{b}$ final state
at 100 TeV.

Our strategy relies on the modeling of the kinematical
distributions of signal and background events, since these provide
the inputs to the MVA discriminant.
%
In this respect, it would be important, having established the key
relevance of the $b\bar{b}b\bar{b}$ channel for the study of
Higgs pair production, to revisit and improve the
theoretical modeling of our signal and background simulation,
in particular using NLO calculations matched to
parton showers both for signal~\cite{Frederix:2014hta,Maierhofer:2013sha}
and for backgrounds~\cite{Alwall:2014hca,Gleisberg:2008ta}.
%

In this work we have considered only the SM production mechanism,
but many BSM scenarios predict deviations
in Higgs pair production, both at the level of total rates
and of
differential distributions.
%
In the absence of new explicit degrees of freedom,
deviations from the SM can be parametrized in
the EFT framework using higher-order
operators~\cite{Azatov:2015oxa,Goertz:2014qta}.
%
Therefore, we plan to study the constraints
on the coefficients of these effective
operators that can be obtained from measurements
of various kinematical distributions
in the $hh\to b\bar{b}b\bar{b}$ process.
%
Note that the higher rates of the $b\bar{b}b\bar{b}$ final state as compared to
other final states, such as
$b\bar{b}\gamma\gamma$, allow for a better constraint upon operators
that modify the high-energy behavior
of the theory, for instance,
it would become possible
to access the tail of the $m_{hh}$ distribution.

As in the case of the extraction of the Higgs
trilinear coupling $\lambda$, such a study
would be a computationally intensive task, since
BSM dynamics will modify the shapes of the kinematical
distributions and thus in principle each point in the EFT parameter
space would require a re-optimization with a newly trained
MVA.
%
In order to explore efficiently the BSM parameters
without having to repeat the full analysis
for each point, modern statistical techniques
such as the Cluster Analysis method proposed
in Ref.~\cite{Dall'Osso:2015aia} might be helpful.

>>>>

In this work we have presented a feasibility study for
 the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the LHC.
%
Our strategy is based on the combination of traditional
cut-based analysis with state-of-the-art multivariate techniques.
%
We take into account 
all relevant backgrounds, in particular
the irreducible $4b$
and the reducible 
$2b2j$ and $4j$ QCD multijets.
%
We have illustrated how the $2b2j$ component leads to
a contribution comparable to that of QCD $4b$ production,
due to a combination of  parton shower effects, $b$-quark 
pair radiation, and selection requirements.
%
We have also demonstrated the robustness of our analysis strategy
under the addition of significant PU.
%
In particular, we have explored two scenarios, $n_{\rm PU}=80$ and
$n_{\rm PU}=150$, and found a comparable overall signal significance
in the two cases.

Combining the contributions from the resolved,
intermediate and boosted categories, we find that, for
$\mathcal{L}=3$ ab$^{-1}$, the
signal significance for
the production of Higgs pairs turns out to be $S/\sqrt{B}\simeq 3$.
%
This indicates that, already from the $b\bar{b}b\bar{b}$
final state alone,
it should be possible to claim observation of Higgs pair production at
the HL-LHC.
%
Our study also suggests possible avenues that the LHC experiments
could explore to further improve this signal significance.
%
One handle would be to reduce the contribution from light and charm
jet mis-identification, ensuring that the irreducible $4b$ background 
dominates over the $2b2j$ component.
%
This would allow to enhance  $S/\sqrt{B}$ almost to the discovery
level, see Table~\ref{table:cutflowMVA_fakes}.
%
It would also be advantageous to improve the $b$-tagging efficiency, allowing
to achieve higher signal yields.
%
Another possibility would be to improve the mass resolution of the Higgs
reconstruction
in high-PU environments, and, more general,
to optimize the PU subtraction
strategy in order
to reduce the impact of PU in the modelling
of kinematic variables and the associated
degradation in the MVA discrimination.
%

Another challenging aspect of the measurement of Higgs pairs
in the $b\bar{b}b\bar{b}$ final state is achieving an efficient
triggering strategy.
%
In order to reduce the rate from background QCD processes sufficiently, while
being able
to access the relevant $p_T$ regimes, (multi-)jet triggers
using $b$-quark tagging information online for one or more jets are
likely to be
necessary.
%
The additional rejection provided by these triggers could
enable events to be selected efficiently, with four
jets down to $p_T=40$ GeV in the resolved category,
and boosted Higgs decays in large-$R$ jets down to jet transverse momenta of
$p_T=200$ GeV.
%
In addition,
good control of the multijet backgrounds and the
experimental systematics of the MVA inputs will be important to achieve
these sensitivities.

Our strategy relies on the modeling of the kinematic
distributions of signal and background events, since these provide
the inputs to the MVA discriminant.
%
In this respect, it would be important, having established the key
relevance of the $b\bar{b}b\bar{b}$ channel for the study of
Higgs pair production, to revisit and improve the
theoretical modeling of our signal and background simulation,
in particular using NLO calculations matched to
parton showers both for signal~\cite{Frederix:2014hta,Maierhofer:2013sha}
and for backgrounds~\cite{Alwall:2014hca,Gleisberg:2008ta}.
%

One important implication of this work is that it should
be possible to significantly
improve  the accuracy on the extraction of
the Higgs trilinear coupling $\lambda$ from
a measurement of the
$\sigma\lp hh\to b\bar{b}b\bar{b}\rp$ cross-section, as compared
to existing estimates.
%
A determination of $\lambda$ in our approach is however
rather
non-trivial, involving
 not only regenerating signal samples
 for a wide range of values of  $\lambda$, but also
 repeating the analysis
optimisation, including the MVA training, for each
of these values.
%
This study is left to a future
publication, where we will also
compare the precision from the $b\bar{b}b\bar{b}$ final state
with the corresponding  precision 
that has been reported from other final states such as
 $b\bar{b}\gamma\gamma$
and $b\bar{b}\tau\tau$.
%
It will also be  interesting to perform
this exercise for a 100 TeV hadron collider~\cite{Barr:2014sga,
  Azatov:2015oxa,Papaefstathiou:2015iba,
  Arkani-Hamed:2015vfh}.
%
While at 100 TeV the
signal yields would be increased, also the (gluon-driven) QCD
multijet background would grow strongly.
%
Revisiting
the present analysis, including the MVA optimization,
at 100 TeV would also allow us
to assess the accuracy of an extraction of the trilinear
coupling $\lambda$ from the $b\bar{b}b\bar{b}$ final state
at 100 TeV.

In this work we have considered only the SM production mechanism,
but many BSM scenarios predict deviations
in Higgs pair production, both at the level of total rates
and of
differential distributions.
%
In the absence of new explicit degrees of freedom,
deviations from the SM can be parametrized in
the EFT framework using higher-order
operators~\cite{Azatov:2015oxa,Goertz:2014qta}.
%
Therefore, we plan to study the constraints
on the coefficients of these effective
operators that can be obtained from measurements
of various kinematic distributions
in the $hh\to b\bar{b}b\bar{b}$ process.
%
Note that the higher rates of the $b\bar{b}b\bar{b}$ final state as compared to
other final states, such as
$b\bar{b}\gamma\gamma$, allow for better constraints upon operators
that modify the high-energy behavior
of the theory, for instance,
it would become possible
to access the tail of the $m_{hh}$ distribution.

As in the case of the extraction of the Higgs
trilinear coupling $\lambda$, such a study
would be a computationally intensive task, since
BSM dynamics will modify the shapes of the kinematic
distributions and thus in principle each point in the EFT parameter
space would require a re-optimization with a newly trained
MVA.
%
In order to explore efficiently the BSM parameters
without having to repeat the full analysis
for each point, modern statistical techniques
such as the Cluster Analysis method proposed
in Ref.~\cite{Dall'Osso:2015aia} might be helpful.

### 2015-12-31 paper-arxiv-v1/sec-intro.tex
Added v2 of paper in repo

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy of $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once
next-to-next-to-leading logarithmic
(NNLL) corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in the gluon-fusion channel
at the LHC have been performed for different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their quantitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$ requires the full integrated luminosity
of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
and should rely on the combination of all relevant final states.

In addition to the gluon-fusion channel, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes
$hhW$ and $hhZ$~\cite{Barger:1988jk,baglio,Cao:2015oxx}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2.0 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
The interplay between  kinematic
distributions for the
extraction of $\lambda$ from the measured
cross-sections, and the role of the associated theoretical
uncertainties, have been intensely scrutinized
recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

@@

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into
$b\bar{b}$
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
final state~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that, for an integrated
luminosity of
$\mathcal{L}=3$ ab$^{-1}$,
a signal significance of around $S/\sqrt{B}\simeq 2.0$ can be obtained.
%
In these analysis, irreducible backgrounds such as $4b$ and
$t\bar{t}$ are included, however the
reducible components, in particular as $bbjj$ and
$jjjj$, are neglected.
%
These can contribute to the signal yield when 
light and charm jets are mis-identified as $b$-jets.
%
Indeed, due to both
selection effects and $b$-quark radiation in the
parton shower, the
contribution of the $2b2j$ process is as significant as
the irreducible $4b$ component.

In this work, we revisit the feasibility of SM Higgs pair production by
gluon-fusion
in the $b\bar{b}b\bar{b}$ final state at the LHC.
%
 Our strategy is based upon a a combination of traditional cut-based
 methods and multivariate analysis (MVA).
  %
  We account for  all relevant
  backgrounds, including the contribution from mis-identified
  light and charm jets.
  %
  We also assess the robustness of our analysis strategy in
  an environment with high pileup (PU).
  %
 Our results indicate that 
  the $b\bar{b}b\bar{b}$ 
final state
alone should allow for the discovery of double Higgs production
  at the HL-LHC.
  %
  We also find that, provided the contamination from light and charm jet
  mis-identification is reduced, the observation of Higgs pairs
  in this final state may be within reach already at Run II with
  $\mathcal{L}=300$ fb$^{-1}$.

>>>>

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy of $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once
next-to-next-to-leading logarithmic
(NNLL) corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in the gluon-fusion channel
at the LHC have been performed for different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their quantitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$ requires the full integrated luminosity
of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
and should rely on the combination of different final states.
%
The interplay between  kinematic
distributions for the
extraction of $\lambda$ from the measured
cross-sections, and the role of the associated theoretical
uncertainties, have been intensely scrutinized
recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

In addition to the gluon-fusion channel, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes
$hhW$ and $hhZ$~\cite{Barger:1988jk,baglio,Cao:2015oxx}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2.0 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%

@@

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into
$b\bar{b}$
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
final state~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that, for an integrated
luminosity of
$\mathcal{L}=3$ ab$^{-1}$,
a signal significance of around $S/\sqrt{B}\simeq 2.0$ can be obtained.
%
In these analysis, irreducible backgrounds such as $4b$ and
$t\bar{t}$ are included, however the
reducible components, in particular $bbjj$ and
$jjjj$, are neglected.
%
These can contribute to the signal yield when 
light and charm jets are mis-identified as $b$-jets.
%
Indeed, due to both
selection effects and $b$-quark radiation in the
parton shower, the
contribution of the $2b2j$ process is as significant as
the irreducible $4b$ component.

In this work, we revisit the feasibility of SM Higgs pair production by
gluon-fusion
in the $b\bar{b}b\bar{b}$ final state at the LHC.
%
 Our strategy is based upon a combination of traditional cut-based
 methods and multivariate analysis (MVA).
  %
  We account for  all relevant
  backgrounds, including the contribution from mis-identified
  light and charm jets.
  %
  We also assess the robustness of our analysis strategy in
  an environment with high pileup (PU).
  %
 Our results indicate that 
  the $b\bar{b}b\bar{b}$ 
final state
alone should allow for the observation of double Higgs production
  at the HL-LHC.
  %

### 2015-12-31 paper-arxiv-v1/sec-mcsamples.tex
Added v2 of paper in repo

Higgs pair production is simulated at leading order (LO) using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored  model~\cite{Maltoni:2014eza}
for gluon-fusion Higgs boson pair production
which includes mass effects
from the
exact form factors for the top-quark triangle and box
loops~\cite{Plehn:1996wb}.
%
Equivalent results can be obtained using
the recently available functionalities
for the calculation of loop-induced processes
in {\tt MadGraph5\_aMC@NLO}~\cite{Hirschi:2015iia}.
%
The calculation is performed in the
$n_f$=4 scheme,  accounting for  $b$-quark mass effects. 
The renormalization and factorization
scales are taken to be $\mu_F=\mu_R=H_T/2$,
with
\be
H_T\equiv \sum_i \sqrt{p_{T,i}^2+m_i^2} \, ,
\ee
the scalar sum of the
transverse masses of all final state particles.
%
For the input parton distribution functions (PDFs) we 
adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$,
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
The Higgs boson couplings
and branching ratios are set to their SM values,
and its mass is taken to be
$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba,Aad:2015zhl}.
%
In the SM, the Higgs trilinear coupling
is given by $\lambda=m_h^2/2v^2$, with
$v\simeq 246$ GeV the Higgs vacuum expectation
value.
%

@@

The LO cross-sections for
the background samples have been rescaled so that the integrated
distributions reproduce known higher-order QCD results.
%
For the $4b$ and $2b2j$ samples NLO/LO $K$-factors of 1.6 and 1.3
respectively have been determined
using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
For the $4j$ sample, we rescale the LO cross-section
using the {\tt BLACKHAT}~\cite{Bern:2011ep}
calculation, resulting in
an NLO/LO $K$-factor of 0.6.
%
Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, leading
to a $K$-factor of 1.4.
%
The $K$-factors that we use to rescale
the signal and background samples are summarised in
Table~\ref{tab:samples}.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 1M & $1.7\cdot10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.1 \cdot10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.7 \cdot 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.7\cdot 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.5\cdot 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Details of the signal and background Monte
  Carlo samples used in this work.
  %
  For top quark production, only the hadronic final state is generated.
  %
  Also provided are the inclusive $K$-factors
  which are applied to reproduce the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

While it is beyond the scope of this work to perform a full
detector simulation, it is important to include an estimate of detector
effects in the analysis, particularly for the finite energy
and angular resolutions which directly
degrade the reconstruction of important kinematical variables, such as
the invariant mass of the Higgs candidates.
%
Here we simulate the finite energy resolution of the ATLAS and CMS
hadronic calorimeters by applying a Gaussian smearing of the transverse
momentum $p_T$ with mean zero and standard deviation $\sigma_E$ for all
final-state particles before jet clustering, that is,
%
\be
\label{eq:smearing}
p_T^{(i)} \, \to \, p_T^{(i)\prime}= \lp 1+ r_i\cdot\sigma_E \rp\, p_T^{(i)} \, , \quad
i=1,\ldots,N_{\rm part} \, ,
\ee
with $r_i$ a univariate Gaussian random number, different for each
of the $N_{\rm part}$ particles in the event.
%
We take as a baseline value for the transverse momentum smearing a
factor of $\sigma_E=5\%$.
%

To account for the finite angular resolution of the calorimeter,
the $\lp \eta,\phi\rp$ plane is divided into regions of
$\Delta \eta \times \Delta \phi=0.1$, and each final state particle
which falls in each of these cells is set to the same $\eta$
and $\phi$ values of the center of the
corresponding cell.
%
Finally, the energy
of each final-state particle
is recalculated from the smeared $p_T^\prime$,
$\eta^\prime$ and $\phi^\prime$ values to ensure that the resulting
four-momentum is that of a light-like particle, since we neglect all
jet constituent masses in this analysis.

>>>>

Higgs pair production is simulated at leading order (LO) using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored  model~\cite{Maltoni:2014eza}
for gluon-fusion Higgs boson pair production
which includes mass effects
from the
exact form factors for the top-quark triangle and box
loops~\cite{Plehn:1996wb}.
%
Equivalent results can be obtained using
the recently available functionalities
for the calculation of loop-induced processes~\cite{Hirschi:2015iia}
in {\tt MadGraph5\_aMC@NLO}.
%
The calculation is performed in the
$n_f$=4 scheme,  accounting for  $b$-quark mass effects. 
The renormalization and factorization
scales are taken to be $\mu_F=\mu_R=H_T/2$,
with
\be
H_T\equiv \sum_i \sqrt{p_{T,i}^2+m_i^2} \, ,
\ee
the scalar sum of the
transverse masses of all final state particles.
%
For the input parton distribution functions (PDFs) we 
adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$,
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
The Higgs boson couplings
and branching ratios are set to their SM values,
and its mass is taken to be
$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba,Aad:2015zhl}.
%
In the SM, the Higgs trilinear coupling
is given by $\lambda=m_h^2/2v^2$, with
$v\simeq 246$ GeV the Higgs vacuum expectation
value.
%

@@

The LO cross-sections for
the background samples have been rescaled so that the integrated
distributions reproduce known higher-order QCD results.
%
For the $4j$ sample, we rescale the LO cross-section
using the {\tt BLACKHAT}~\cite{Bern:2011ep}
calculation, resulting in
an NLO/LO $K$-factor of 0.6.
%
For the $4b$ and $2b2j$ samples NLO/LO $K$-factors of 1.6 and 1.3
respectively have been determined
using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, leading
to a $K$-factor of 1.4.
%
The $K$-factors that we use to rescale
the signal and background samples are summarised in
Table~\ref{tab:samples}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh\to 4b$ &  {\tt MadGraph5\_aMC@NLO} & 1M & $6.2\cdot10^{-3}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA} & 3M &$1.1 \cdot10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA} & 3M & $2.7 \cdot 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA} & 3M  & $9.7\cdot 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA} & 3M & $2.5\cdot 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Details of the signal and background Monte
  Carlo samples used in this work.
  %
  Also provided are the inclusive $K$-factors
  which are applied to reproduce the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

While it is beyond the scope of this work to perform a full
detector simulation, it is important to include an estimate of detector
effects in the analysis, particularly for the finite energy
and angular resolutions which directly
degrade the reconstruction of important kinematic variables, such as
the invariant mass of the Higgs candidates.
%
Here we simulate the finite energy resolution of the ATLAS and CMS
hadronic calorimeters by applying a Gaussian smearing of the transverse
momentum $p_T$ with mean zero and standard deviation $\sigma_E$ for all
final-state particles before jet clustering, that is,
%
\be
\label{eq:smearing}
p_T^{(i)} \, \to \, p_T^{(i)\prime}= \lp 1+ r_i\cdot\sigma_E \rp\, p_T^{(i)} \, , \quad
i=1,\ldots,N_{\rm part} \, ,
\ee
with $r_i$ a univariate Gaussian random number, different for each
of the $N_{\rm part}$ particles in the event.
%
We take as a baseline value for the transverse momentum smearing a
factor of $\sigma_E=5\%$.
%

To account for the finite angular resolution of the calorimeter,
the $\lp \eta,\phi\rp$ plane is divided into regions of
$\Delta \eta \times \Delta \phi=0.1\times 0.1$,
and each final state particle
which falls in each of these cells is set to the same $\eta$
and $\phi$ values of the center of the
corresponding cell.
%
Finally, the energy
of each final-state particle
is recalculated from the smeared $p_T^\prime$,
$\eta^\prime$ and $\phi^\prime$ values to ensure that the resulting
four-momentum is that of a light-like particle, since we neglect all
jet constituent masses in this analysis.
